---
output:
  officedown::rdocx_document: 
    reference_docx: style_example.docx
    pandoc_args: ["--metadata-file=header.yaml"]
csl: "cite/citestyle.csl"
bibliography: "cite/bibliography.bib"
---

# R setup for Markdown

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE, message = FALSE)
library(officedown)
library(officer)
#library(pandoc)
library(rmarkdown)

# This downloads text chunks from Google Drive!
source(here::here("get_files_from_gdrive.R"))

# This defines some constants that we can use to populate the report.
constantvalue <- 5
```

# Components
There are three components in the header:

1. `style_example.docx` is a Word file with the styles you want to use. Edit the layout options in this file to get different styles for Header 1, etc.
2. `header.yaml` is the basic yaml header for the doc.
3. `citestyle.csl` has the citation formatting
4. `bibliography.bib` is your bibliography. Refer to this when tagging references in your doc.

# Example of imported text.

Using "children," you can have a hybrid Markdown file containing both regular Markdown in the .Rmd file, and text chunks you've downloaded from google drive. So! This here is text I typed straight into the Rmd, and ...

```{r child=here::here("gdrive_downloads","TextChunk1.Rmd")}
```

# Tables
```{r tab.cap='This is a caption for a table. A hot tip for tables and figures is that Markdown hates underscores in your figure ids. So if you assign a figure id, use hyphens instead.', tab.id='table-basic',  tab.cap.style = "Table Caption"}
tab1 <- data.frame(Label = c("A","B","C"),
                   Number = rnorm(n = 3,mean = 1,sd = .5))
tab1
```

# Figures
```{r fig.cap='This is a caption for a figure.', fig.id='fig-basic',  tab.cap.style = "Figure Caption"}
plot(1:10,1:10)
```